A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex
turker quality summary table

%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
\begin{figure}[h]
\footnotesize
\begin{tabular}{lrlrlr}\hline\hline
%Language&\# Turkers\\
\hline
English&591&	French&63&	Vietnamese&34\\
Tamil&253&	Polish&61&	Macedonian&31\\
Malayalam&219&	Urdu&56&	Cebuano&29\\
Hindi&149&	Tagalog&54&	Swedish&26\\
Spanish&131&	Marathi&48&	Bulgarian&25\\
Telugu&87&	Russian&44&	Hungarian&23\\
Chinese&86&	Italian&43&	Swahili&23\\
Romanian&85&	Bengali&41&	Thai&22\\
Portuguese&82&	Gujarati&39&	Catalan&22\\
Arabic&74&	Hebrew&38&	Lithuanian&21\\
Kannada&72&	Dutch&37&	Punjabi&21\\
German&66&	Turkish&35&	Others &$\leq$20\\
\hline\hline
\end{tabular}
\normalsize
\caption{XXX}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
%\begin{figure}[h]
%\centering
%\includegraphics[width=\linewidth]{figures/natlang-pie}
%\caption{Self-reported native language of 3,154 bilingual turkers}
%\label{lang-pie}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background and Related Work}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce. MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs),which hints at its origins.  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

@@

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/Turkermap-color-cropped}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of  5,284 workers in our study.  The size of the circles represents the number of worker from each country.  The two largest are India (2,022 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-scatter-avgTurkers-country-labeled}
\caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.
%Self-reported country information is typically reliable. Three quarters of Turkers who reported their native language reported a single native language consistently across all assignments, and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language.  Less than 5\% of Turkers gave unreasonable responses with 3 or more native languages. Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.

>>>>

%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{cc}\hline\hline
Language&\# Turkers\\
\hline
English&591\\
Tamil&253\\
Malayalam&219\\
Hindi&149\\
Spanish&131\\
Telugu&87\\
Chinese&86\\
Romanian&85\\
Portuguese&82\\
Arabic&74\\
Kannada&72\\
German&66\\
French&63\\
Polish&61\\
Urdu&56\\
Tagalog&54\\
Marathi&48\\
Russian&44\\
Italian&43\\
Bengali&41\\
Gujarati&39\\
Hebrew&38\\
Dutch&37\\
Turkish&35\\
Vietnamese&34\\
Macedonian&31\\
Cebuano&29\\
Swedish&26\\
Bulgarian&25\\
Hungarian&23\\
Swahili&23\\
Thai&22\\
Catalan&22\\
Lithuanian&21\\
Punjabi&21\\
Other($\leq$ 20 per language)&423\\
\hline\hline
\end{tabular}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\section{Background and Related Work}
%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
%\begin{figure*}[h]
%\centering
%\includegraphics[width=7in]{figures/natlang-pie}
%\caption{Self-reported native language of 3,154 bilingual turkers}
%\label{lang-pie}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce. MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs),which hints at its origins.  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

@@

@@

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\centering
\include{summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled}
\caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

### 2013-02-20 writeup/summary.tex
turker quality summary table

\begin{figure}[h]
\centering
\begin{tabular}{llcclccc}
\multicolumn{8}{c}{Number of Turkers per language}\\
\hline\hline
&&All&\multicolumn{2}{c}{cl match}&\multicolumn{2}{c}{quality (dict size)}\\
&&&total&by country&in region&out of region\\
\hline\hline
hi&Hindi&312&300&India(285) Uae(5) &\textbf{0.5387} (9908)&0.4728 (41) \\
&&&&Scotland (5) Other (5) &&&\\
&&&&&&&\\
ta&Tamil&294&278&India(271) US(3) &\textbf{0.5528} (9974)&0.54 (5) \\
&&&&Canada (2) Other (2) &&&\\
&&&&&&&\\
ml&Malayalam&245&235&India(224) Uae(6) &0.4759 (9966)&\textbf{0.5523} (25)\\
&&&&US (3) Other (2) &&&\\
&&&&&&&\\
es&Spanish&235&206&US(131) Mexico(18) &\textbf{0.2711} (9768)&0.2677 (67) \\
&&&&Westspain (14) Other (43) &&&\\
&&&&&&&\\
fr&French&202&183&India(68) US(48) &0.2907 (9514)&\textbf{0.3063} (386)\\
&&&&France (25) Other (42) &&&\\
&&&&&&&\\
de&German&163&100&Germany(51) US(29) &\textbf{0.3527} (8892)&0.306 (1029) \\
&&&&Austria (9) Other (11) &&&\\
&&&&&&&\\
it&Italian&159&98&Italy(44) US(32) &\textbf{0.3221} (7885)&0.2734 (1870) \\
&&&&Romania (9) Other (13) &&&\\
&&&&&&&\\
zh&Chinese&150&130&US(80) Singapore(15) &0.1821 (3510)&\textbf{0.4113} (137)\\
&&&&China (14) Other (21) &&&\\
&&&&&&&\\
ms&Malay&128&15&Malaysia(8) Singapore(4) &\textbf{0.2946} (6143)&0.2755 (3623) \\
&&&&US (2) Other (1) &&&\\
&&&&&&&\\
ga&Irish&121&58&US(41) Ireland(13) &\textbf{0.3201} (3775)&0.2612 (6139) \\
&&&&Scotland (4) &&&\\
&&&&&&&\\
\hline\hline
\end{tabular}
\end{figure}

>>>>

\begin{figure}[h]
\centering
*** PLACE HOLDER NUMBERS; NUMBERS WITH ACCPETED HITS ONLY STILL RUNNING ***
\begin{tabular}{llcccccc}
\multicolumn{8}{c}{Number of Turkers per language}\\
\hline\hline
&&Total \# Turkers&\multicolumn{2}{c}{\# Turkers in language region}&\multicolumn{2}{c}{Avg. Turker quality (Dictionary size)}\\
&&&Overall&By country&In region&Out of region\\
\hline\hline
hi&Hindi&312&300&India (285) Uae (5) &\textbf{0.5387} (9908)&0.4728 (41) \\
&&&&Scotland (5) Other (5) &&&\\
&&&&&&&\\
ta&Tamil&294&278&India (271) US (3) &\textbf{0.5528} (9974)&0.54 (5) \\
&&&&Canada (2) Other (2) &&&\\
&&&&&&&\\
ml&Malayalam&245&235&India (224) Uae (6) &0.4759 (9966)&\textbf{0.5523} (25)\\
&&&&US (3) Other (2) &&&\\
&&&&&&&\\
es&Spanish&235&206&US (131) Mexico (18) &\textbf{0.2711} (9768)&0.2677 (67) \\
&&&&Westspain (14) Other (43) &&&\\
&&&&&&&\\
fr&French&202&183&India (68) US (48) &0.2907 (9514)&\textbf{0.3063} (386)\\
&&&&France (25) Other (42) &&&\\
&&&&&&&\\
de&German&163&100&Germany (51) US (29) &\textbf{0.3527} (8892)&0.306 (1029) \\
&&&&Austria (9) Other (11) &&&\\
&&&&&&&\\
it&Italian&159&98&Italy (44) US (32) &\textbf{0.3221} (7885)&0.2734 (1870) \\
&&&&Romania (9) Other (13) &&&\\
&&&&&&&\\
zh&Chinese&150&130&US (80) Singapore (15) &0.1821 (3510)&\textbf{0.4113} (137)\\
&&&&China (14) Other (21) &&&\\
&&&&&&&\\
ms&Malay&128&15&Malaysia (8) Singapore (4) &\textbf{0.2946} (6147)&0.2755 (3619) \\
&&&&US (2) Other (1) &&&\\
&&&&&&&\\
ga&Irish&121&58&US (41) Ireland (13) &\textbf{0.3201} (3775)&0.2612 (6139) \\
&&&&Scotland (4) &&&\\
&&&&&&&\\
\hline\hline
\end{tabular}
\end{figure}
